Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-04 paper.tex
Remove a line
Remove not so relevant line

The Simics simulator uses demand paging for simulated environments, which means
that memory is only allocated when it is used. As long as the working set of
the target system fits in the host memory, performance will be tolerable.
However, in our work, we wish to study OS behavior under workloads that
actually use all available memory. Thus, the usefulness of demand paging is
greatly reduced because swapping causes disk latency to become the main
performance bottleneck. Moreover, the performance overhead of simulators like
Simics tends to be impractical because system state needs to be maintained by
the simulator \cite{simics}. We do not explore simulation further because it
can be orders of magnitude slower than native execution, making it infeasible
for studying large workloads or systems \cite{2kmachine}. However, the Simics
simulator illustrates the usefulness of memory management techniques such as
demand paging and the potential overheads of swapping.

>>>>

The Simics simulator uses demand paging for simulated environments.
As long as the working set of
the target system fits in the host memory, performance will be tolerable.
However, in our work, we wish to study OS behavior under workloads that
actually use all available memory. Thus, the usefulness of demand paging is
greatly reduced because swapping causes disk latency to become the main
performance bottleneck. Moreover, the performance overhead of simulators like
Simics tends to be impractical because system state needs to be maintained by
the simulator \cite{simics}. We do not explore simulation further because it
can be orders of magnitude slower than native execution, making it infeasible
for studying large workloads or systems \cite{2kmachine}.
